Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-07-25 README.qmd
Add DOI badges
Add preprint badge

<!-- badges: start -->
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fy8ked-blue)](https://doi.org/10.31235/osf.io/y8ked) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FAQVNK-blue)](https://doi.org/10.17605/OSF.IO/AQVNK) [![Code DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.12817616.svg)](https://doi.org/10.5281/zenodo.12817616)
<!-- badges: end -->
